Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-04-14 Article.Rmd
Data manipulation and vizualisation of year, design and location of studies

knitr::knit_exit()

@@

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load required packages :
library(tidyverse)
library(readr)

@@

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_data.R", local = knitr::knit_global())
source("./scripts/create_design_data.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())

@@

>>>>

@@

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)

@@

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_design.R", local = knitr::knit_global())
source("./scripts/create_design_data.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())
source("./scripts/create_sample.R", local = knitr::knit_global())

#Create the plot 
source("./scripts/create_plot_year.R", local = knitr::knit_global())

@@

The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in \@ref(fig:PlotYear).

```{r PlotYear, fig.cap = "Plot of the cumulative number of studies published yearly, grouped by continent (A) and design (B)"}

knitr::include_graphics("./Output/Plots/Plot_Year.png")

Out of the 104 quantitative and qualitative studies included, most were conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`). The majority of the remaining studies were then located in Asia (N = `r Asia_studies`) or in Europe (N = `r Europe_studies`). South America and Africa were the least represented continents, with only `r South_America_studies` and `r Africa_studies` studies respectively.
